---
output: 
  html_document:
    keep_md: true
---

# flares

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
```

```{r, include=FALSE}
library(tidyverse)
library(magrittr)
library(lubridate)
library(sf)
library(maps)
library(gridExtra)
library(cowplot)
library(RColorBrewer)
library(ggthemes)
library(tidycensus)
library(viridis)
#### include your census api key
#census_api_key('<your_key>', install = TRUE)
```

```{r, include=FALSE}
#### Read fracking well data
# Filter 2017 to compare with disperseR results
flares <- read_csv("../data/input/tx-tracts-vnf-nightly.csv")

flares %<>%
  mutate(STATEFP = as.character(STATEFP), 
         #COUNTYFP = as.character(COUNTYFP), 
         #TRACTCE = as.character(TRACTCE),
         GEOID = as.character(GEOID), 
         year = year(date), 
         month = month(date)) %>% 
  filter(year == 2017)
```

```{r, include=FALSE}
#### read state shapefile
states_sf <- st_as_sf(map("state", plot = FALSE, fill = TRUE))
crs_ <- st_crs(states_sf)
```

<!-- ```{python} -->
<!-- import wget -->
<!-- from zipfile import ZipFile -->
<!-- import os -->

<!-- url = 'https://www2.census.gov/geo/tiger/TIGER2016/TRACT/tl_2016_48_tract.zip' -->
<!-- wget.download(url, os.path.expanduser('~/tmp')) -->
<!-- file_name = os.path.expanduser('~/tmp/tl_2016_48_tract.zip') -->
<!-- ZipFile(file_name, 'r').extractall(os.path.expanduser('~/tmp/tl_2016_48_tract/')) -->
<!-- os.system("ls ~/tmp/tl_2016_48_tract/") -->
<!-- ``` -->

```{r, include=FALSE}
#### read tracts shapefile
tracts_sf <- st_read("~/tmp/tl_2016_48_tract/tl_2016_48_tract.shp")
tracts_sf <- tracts_sf %>% 
  dplyr::filter(STATEFP == "48")
tracts_sf <- st_transform(tracts_sf, crs_)
```

```{r, include=FALSE}
#### get tracts population
v18 <- load_variables(2018, "acs5", cache = TRUE)
# View(v18)

# Estimate!!Total
tract_acs <- get_acs(year = 2018,
                     geography = "tract",
                     variables = "B01001_001",
                     state = "TX",
                     geometry = FALSE)
tract_acs %<>% 
  rename(pop = estimate)
```

```{r, include=FALSE}
#### join tracts and flares
# all flares GEOIDs in shapefile
# sum(!flares$GEOID %in% tracts_sf$GEOID)

tracts_sf %<>% 
  left_join(flares %>% 
              group_by(GEOID) %>% 
              summarise(tot_flares = sum(flares)))
```

```{r, include=FALSE}
#### join tracts and population
# all shapefile GEOIDs in acs query
# sum(!tracts_sf$GEOID %in% tract_acs$GEOID) 

tracts_sf %<>% 
  left_join(tract_acs %>% 
              select(GEOID, pop))
```

```{r, include=FALSE}
#### read cbsa data
cbsa <- read_csv("../data/input/cbsa.csv")

cbsa %<>% 
  mutate(cbsa = as.character(cbsa), 
         fips = as.character(fips))
```

```{r, include=FALSE}
#### join tracts_sf and cbsa data
tracts_sf %<>% 
  mutate(fips = paste0(STATEFP, COUNTYFP))

# some tracts are not listed in the cbsa file
#unique(tracts_sf$fips[!tracts_sf$fips %in% cbsa$fips])

tracts_sf %<>% 
  left_join(cbsa) %>% 
  mutate(cbsa = if_else(is.na(cbsa), COUNTYFP, cbsa), 
         cbsa_name = if_else(is.na(cbsa_name), fips, cbsa_name)
         ) %>% 
  group_by(cbsa) %>% 
  mutate(pop_cbsa = sum(pop)) %>% 
  ungroup()
```

A total of `r prettyNum(sum(flares$flares), big.mark = ",")` flares were reported in 2017.

A total of `r sprintf('%s', length(unique(flares$GEOID)))` tracts were exposed.

## Total flares per month time series

```{r}
flares %<>% 
  mutate(yyyy_mm = format(as.Date(date), "%Y_%m"))

flares %>% 
  group_by(yyyy_mm) %>% 
  summarise(flares = sum(flares)) %>% 
ggplot() + 
  geom_line(aes(x = ym(yyyy_mm), y = flares, color = flares)) +
  theme_cowplot() + 
  labs(title = "Total flares per month", x = "")
```

## Total flares per tract

* total flares summary

```{r}
tot_flares_ <- tracts_sf$tot_flares
summary(tot_flares_)
```

* Color scheme in deciles.

```{r}
tracts_sf$tot_flares_cut <- cut(tot_flares_, 
                                quantile(tot_flares_, seq(0,1,.1), na.rm = T), 
                                include.lowest = T) 

tracts_sf %>%  
  filter(!is.na(tot_flares)) %>% 
ggplot() + 
  geom_sf(data = filter(states_sf, ID == "texas")) + 
  geom_sf(aes(fill = tot_flares_cut), colour = NA, lwd = 0) + 
  scale_fill_viridis_d() +
  theme_map() + 
  theme(legend.position = "right") + 
  labs(title = "Total flares per tract")
```

## Total flares per tract area normalized

* flares per sq km summary

```{r}
tracts_sf %<>% 
  mutate(norm_flares = tot_flares / ALAND * 1e6) #ALAND in tiger filers is reported in sq meters

summary(tracts_sf$norm_flares)
```

* highest 5% in red

```{r}
x_sf <- tracts_sf
x_sf$fill_var <-  st_drop_geometry(x_sf) %>% pull("norm_flares")
q95 <- quantile(x_sf$fill_var, probs = .95, na.rm = TRUE)
x_sf_ <- x_sf[x_sf$fill_var > q95,] %>%  
  filter(!is.na(fill_var))
x_sf <- x_sf[x_sf$fill_var <= q95,] %>%  
  filter(!is.na(fill_var))

ggplot() +
    geom_sf(data = filter(states_sf, ID == "texas")) + 
    geom_sf(data = x_sf_, fill = "red", colour = "red") + 
    geom_sf(data = x_sf, aes(fill = fill_var), colour = NA, lwd = 0) +
  scale_fill_viridis_c(trans = "sqrt") +
  theme_map() + 
  labs(title = "Total flares per tract area normalized", 
       fill = "highest 5%\nin red")
```

## Monthly flares per tract area normalized

* summary

```{r}
flares %<>% 
  left_join(tracts_sf %>% 
              st_drop_geometry() %>% 
              select(GEOID, ALAND))

flares %<>% 
  group_by(yyyy_mm, GEOID, ALAND) %>% 
  mutate(GEOID_month_tot_flares = sum(flares), 
         GEOID_month_norm_flares = GEOID_month_tot_flares / ALAND * 1e6)

summary(flares$GEOID_month_norm_flares)
```

```{r, include=FALSE}
# generate tract_flares_maps.pdf summary
xx <- flares
xx$fill_var <- xx$GEOID_month_norm_flares
q95 <- quantile(xx$fill_var, probs = .95, na.rm = TRUE)
xx_ <- xx[xx$fill_var > q95,]
xx <- xx[xx$fill_var <= q95,]
myPalette <- colorRampPalette(rev(brewer.pal(11, "Spectral")))
sc <- scale_fill_gradientn(colours = myPalette(100), 
                             limits=c(min(xx$fill_var), max(xx$fill_var)))
  
tract_flares_maps <- list()
yyyy_mm_ <- sort(unique(flares$yyyy_mm))

y <- yyyy_mm_[1]
x_sf <- tracts_sf %>% 
    left_join(xx %>% 
                filter(yyyy_mm == y)) %>% 
    filter(!is.na(fill_var))
x_sf_ <- tracts_sf %>% 
    left_join(xx_ %>% 
                filter(yyyy_mm == y)) %>% 
    filter(!is.na(fill_var))

p <- ggplot() +
    geom_sf(data = filter(states_sf, ID == "texas")) + 
    geom_sf(data = x_sf_, fill = "black", colour = "black") + 
    geom_sf(data = x_sf, aes(fill = fill_var), colour = NA, lwd = 0) + 
    sc + 
  labs(fill = "highest 5%\nin black")
tract_flares_maps[[1]] <- get_legend(p)

for(y in yyyy_mm_) {
  x_sf <- tracts_sf %>% 
    left_join(xx %>% 
                filter(yyyy_mm == y)) %>% 
    filter(!is.na(fill_var))
  
  x_sf_ <- tracts_sf %>% 
    left_join(xx_ %>% 
                filter(yyyy_mm == y)) %>% 
    filter(!is.na(fill_var))
  
    tract_flares_maps[[y]] <- ggplot() +
    geom_sf(data = filter(states_sf, ID == "texas")) + 
    geom_sf(data = x_sf_, fill = "black", colour = "black") + 
    geom_sf(data = x_sf, aes(fill = fill_var), colour = NA, lwd = 0) + 
    sc + 
    theme_map() +
    theme(legend.position = "none") + 
    labs(title = y)
}

tract_flares_maps <- marrangeGrob(tract_flares_maps, 
                           nrow = 4, ncol = 2, 
                           left = "", top = "Area normalized flares per tract in yyyy-mm")
ggsave("./flares_output/tract_flares_maps.pdf", 
       tract_flares_maps, width = 15, height = 25, units = "cm")
```

## Monthly mean flares per tract area summarised

* summary

```{r}
tracts_sf %<>% 
  left_join(flares %>% 
              group_by(GEOID) %>% 
              summarise(mu_norm_flares = mean(GEOID_month_norm_flares))
            )

summary(tracts_sf$mu_norm_flares)
```


```{r}
x_sf <- tracts_sf
x_sf$fill_var <-  st_drop_geometry(x_sf) %>% pull("mu_norm_flares")
q95 <- quantile(x_sf$fill_var, probs = .95, na.rm = TRUE)
x_sf_ <- x_sf[x_sf$fill_var > q95,] %>%  
  filter(!is.na(fill_var))
x_sf <- x_sf[x_sf$fill_var <= q95,] %>%  
  filter(!is.na(fill_var))

ggplot() +
    geom_sf(data = filter(states_sf, ID == "texas")) + 
    geom_sf(data = x_sf_, fill = "red", colour = "red") + 
    geom_sf(data = x_sf, aes(fill = fill_var), colour = NA, lwd = 0) +
  scale_fill_viridis_c(trans = "sqrt") +
  theme_map() + 
  labs(title = "Mean of monthly flares per tract area normalized", 
       fill = "highest 5%\nin red")
```

## Cap exposure to flares

A total of `r prettyNum(sum(tracts_sf$pop[!is.na(tracts_sf$tot_flares)]), big.mark = ",")` people live in tracts where flares events occurred.

In general, tracts with higher number of flares are less populated. 

```{r}
tracts_sf %>% 
  filter(!is.na(tot_flares)) %>% 
ggplot() + 
  geom_point(aes(x=tot_flares, pop), color = "blue") + 
  labs(title = "Scatterplot", y = "population", x = "total flares") + 
  theme_cowplot() + 
  scale_y_continuous(labels = scales::comma)
```

```{r}
tracts_sf %>% 
  filter(!is.na(tot_flares)) %>% 
  arrange(pop) %>% 
  mutate(cumsum_pop = cumsum(pop), 
         cumsum_flares = cumsum(tot_flares)) %>% 
ggplot() + 
  geom_point(aes(y=cumsum_flares, x=cumsum_pop), color = "blue", shape = 4) +
  geom_line(aes(y=cumsum_flares, x=cumsum_pop), size = 0.1) + 
  labs(y = "accumulated flares", x = "accumulated population") + 
  theme_cowplot() + 
  scale_y_continuous(labels = scales::comma) + 
  scale_x_continuous(labels = scales::comma)
```


<!-- ```{r} -->
<!-- tracts_sf %>%  -->
<!--   filter(!is.na(tot_flares)) %>%  -->
<!--   arrange(pop_cbsa) %>%  -->
<!--   mutate(cumsum_pop = cumsum(pop),  -->
<!--          cumsum_flares = cumsum(tot_flares)) %>%  -->
<!-- ggplot() +  -->
<!--   geom_point(aes(x=cumsum_flares, cumsum_pop, color = cbsa_name)) + -->
<!--   geom_line(aes(x=cumsum_flares, cumsum_pop)) -->
<!-- ``` -->

```{r, include=FALSE}
# generate cbsa_flares_map.pdf summary
flares %<>% 
  mutate(fips = paste0(STATEFP, COUNTYFP)) %>% 
  left_join(cbsa)  %>% 
  mutate(cbsa = if_else(is.na(cbsa), COUNTYFP, cbsa), 
         cbsa_name = if_else(is.na(cbsa_name), fips, cbsa_name)
         )

x_sf <- tracts_sf
x_sf$fill_var <-  st_drop_geometry(x_sf) %>% pull("norm_flares")
q95 <- quantile(x_sf$fill_var, probs = .95, na.rm = TRUE)
x_sf_ <- x_sf[x_sf$fill_var > q95,] %>%  
  filter(!is.na(fill_var))
x_sf <- x_sf[x_sf$fill_var <= q95,] %>%  
  filter(!is.na(fill_var))

myPalette <- colorRampPalette(rev(brewer.pal(11, "Spectral")))
sc <- scale_fill_gradientn(colours = myPalette(100), 
                             limits=c(min(x_sf$norm_flares, na.rm = T), 
                                      max(x_sf$norm_flares, na.rm = T)))
cbsa_ <- tracts_sf %>% 
  st_drop_geometry() %>% 
  mutate(exposed = (!is.na(tot_flares)), 
         exposed_pop = pop * exposed) %>% 
  group_by(cbsa, cbsa_name, pop_cbsa) %>% 
  summarise(tot_flares = sum(tot_flares, na.rm = T), 
            exposed_pop = sum(exposed_pop),
            n = n(), 
            exposed = sum(exposed)) %>% 
  filter(tot_flares > 0) %>%
  arrange(desc(pop_cbsa))

cbsa_flares_map <- list()

for(i in 1:nrow(cbsa_)) {
  xx <- tracts_sf %>% 
    filter(cbsa == cbsa_$cbsa[i])
  yy <- flares %>% 
    filter(cbsa == cbsa_$cbsa[i])
  
  pa1 <- xx %>% 
    ggplot() + 
    geom_sf(data = filter(states_sf, ID == "texas")) + 
    geom_sf(aes(fill = norm_flares), colour = NA, lwd = 0) +
    theme_map() + 
    theme(legend.position = "left") + 
    sc + 
    labs(title = cbsa_$cbsa_name[i], 
         subtitle = paste("total flares:", 
                          prettyNum(cbsa_$tot_flares[i], big.mark = ",")),
         fill = "total\nflares\narea\nnormalized")

  pa2 <- xx %>% 
    ggplot() + 
    geom_sf(aes(fill = norm_flares), colour = NA, lwd = 0) +
    theme_map() + 
    theme(legend.position = "none") + 
    sc  + 
    labs(subtitle = paste("number of tracts:", 
                          prettyNum(cbsa_$n[i], big.mark = ","), 
                          "\nnumber of exposed tracts:", 
                          prettyNum(cbsa_$exposed[i], big.mark = ",")))
  
  pa <- plot_grid(pa1, pa2, ncol = 2)
  
  pb <- yy %>%  
    group_by(yyyy_mm) %>% 
    summarise(flares = sum(flares)) %>% 
    ggplot() + 
    geom_line(aes(x = ym(yyyy_mm), y = flares, color = flares)) + 
    theme_cowplot() + 
    labs(title = "Total flares per month", x = "")
    
  # pb <- xx %>%  
  #   mutate(tot_flares = if_else(is.na(tot_flares), 0, tot_flares)) %>% 
  #   arrange(tot_flares, pop) %>% 
  #   mutate(cumsum_pop = cumsum(pop), 
  #          cumsum_flares = cumsum(tot_flares)) %>% 
  # ggplot() + 
  #   geom_point(aes(x=cumsum_pop, y = cumsum_flares), color = "blue", 
  #              size = 0.5, shape = 4) + 
  #   geom_line(aes(x=cumsum_pop, y = cumsum_flares), size = 0.1) + 
  #   theme_cowplot() + 
  #   labs(subtitle = paste("total population:", 
  #                         prettyNum(cbsa_$pop_cbsa[i], big.mark = ","), 
  #                         "\nexposed population:", 
  #                         prettyNum(cbsa_$exposed_pop[i], big.mark = ",")), 
  #        y = "accumulated flares", 
  #        x = "accumulated population") + 
  #   scale_y_continuous(labels = scales::label_number(accuracy = 1, big.mark = ',')) + 
  #   scale_x_continuous(labels = scales::label_number(accuracy = 1, big.mark = ','))
  
  cbsa_flares_map[[i]] <- plot_grid(pa, pb, nrow = 2)
}
cbsa_flares_map <- marrangeGrob(cbsa_flares_map, 
                           nrow = 2, ncol = 1, 
                           left = "", top = "")
ggsave("./flares_output/cbsa_flares_map.pdf", 
       cbsa_flares_map, width = 15, height = 25, units = "cm")
```


<!-- ```{r, include=FALSE} -->
<!-- flares_cbsa <- flares %>% -->
<!--   group_by(yyyy_mm, cbsa) %>% -->
<!--   summarise(flares = sum(flares)) -->
<!-- myPalette <- colorRampPalette(rev(brewer.pal(11, "Spectral"))) -->
<!-- sc <- scale_color_gradientn(colours = myPalette(100), -->
<!--                              limits=c(min(flares_cbsa$flares), -->
<!--                                       max(flares_cbsa$flares))) -->

<!-- cbsa_flares_ts <- list() -->
<!-- cbsa_sf %<>% -->
<!--   arrange(desc(flares_per_cap)) -->
<!-- #i = 1 -->
<!-- for(i in 1:nrow(cbsa_sf)) { -->
<!--   cbsa_ <- cbsa_sf$cbsa[i] -->
<!--   cbsa_name_ <- cbsa_sf$cbsa_name[i] -->
<!--   flares_per_cap_ <- cbsa_sf$flares_per_cap[i] -->

<!--   map <- cbsa_sf %>% -->
<!--     filter(cbsa == cbsa_) %>% -->
<!--     ggplot() + -->
<!--     geom_sf(data = filter(states_sf, ID == "texas")) + -->
<!--     geom_sf(aes(fill = cbsa_)) + -->
<!--     theme_map() + -->
<!--     theme(legend.position = "none") + -->
<!--     labs(title = "flares per cap:", -->
<!--          subtitle = round(flares_per_cap_, digits = 2)) -->

<!--   ts <- flares_cbsa %>% -->
<!--     filter(cbsa == cbsa_) %>% -->
<!--     ggplot() + -->
<!--     geom_point(aes(x = ym(yyyy_mm), y = flares, color = flares)) + -->
<!--     geom_line(aes(x = ym(yyyy_mm), y = flares, color = flares)) + -->
<!--     sc + -->
<!--     theme_cowplot() + -->
<!--     xlim(c(min(ym(flares_cbsa$yyyy_mm)), max(ym(flares_cbsa$yyyy_mm)))) + -->
<!--     theme(legend.position = "none") + -->
<!--     labs(title = cbsa_name_, x = "") -->

<!--   cbsa_flares_ts[[i]] <- plot_grid(map, ts, ncol = 2, rel_widths = c(0.2, 0.8)) -->
<!-- } -->
<!-- cbsa_flares_ts <- marrangeGrob(cbsa_flares_ts, -->
<!--                            nrow = 3, ncol = 1, -->
<!--                            left = "", top = "CBSA's sorted by flares per capita") -->
<!-- ggsave("./flares_output/cbsa_flares_ts.pdf", -->
<!--        cbsa_flares_ts, width = 15, height = 25, units = "cm") -->
<!-- ``` -->
