# Hyads

```{r}
library(tidyverse)
library(magrittr)
library(lubridate)
library(sf)
library(viridis)
library(ggthemes)

disperser_input <- read_rds("../data/jobs_input/disperser_input.rds")
tracts_sf <- read_rds("../data/preprocessed/tracts_sf.rds")
```

## 2017 Monthly Hyads

```{r}
links <- read_rds("../data/jobs_output/linked_counties_2017_1_2.rds") |>
  rbind(read_rds("../data/jobs_output/linked_counties_2017_3_4.rds")) |>
  rbind(read_rds("../data/jobs_output/linked_counties_2017_5_6.rds")) |>
  rbind(read_rds("../data/jobs_output/linked_counties_2017_7_8.rds")) |>
  rbind(read_rds("../data/jobs_output/linked_counties_2017_9_10.rds")) |>
  rbind(read_rds("../data/jobs_output/linked_counties_2017_11_12.rds"))

links %<>% 
  rename(GEOID = geoid, hyads = N, ym = month)  %>% 
  mutate(year = as.integer(str_sub(ym, 1, 4)),
         month = as.integer(str_sub(ym, 5, -1)),
         date = ymd(sprintf("%04d%02d01", year, month)))
```

```{r}
xx <- disperser_input %>% 
  distinct(ID, year, month, start_day, w) %>% 
  group_by(ID, year, month) %>% 
  summarise(w = sum(w))  %>% 
  left_join(
    tracts_sf %>% 
      st_drop_geometry() %>% 
      rename(ID = GEOID) %>% 
      dplyr::select(ID, basin) 
  ) %>% 
  rename(basin_ID = basin)

hyads_months <- left_join(links, xx) %>% 
  group_by(GEOID, ym, year, month, basin_ID) %>% 
  summarise(
    unweighted_hyads = sum(hyads),
    weighted_hyads = sum(w * hyads)
  )
```

* Unweighed hyads values summary in each basin for all tracts-month with positive exposure within 2017

```{r}
tapply(hyads_months$unweighted_hyads, hyads_months$basin_ID, summary)
```

```{r}
hyads_months %>% 
  ggplot() +
  geom_violin(aes(x=basin_ID, y=unweighted_hyads)) + 
  scale_y_log10(labels = scales::comma)
```

* Weighed hyads values summary in each basin for all tracts-month with positive exposure within 2017

```{r}
tapply(hyads_months$weighted_hyads, hyads_months$basin_ID, summary)
```

```{r}
hyads_months %>% 
  ggplot() +
  geom_violin(aes(x=basin_ID, y=weighted_hyads)) + 
  scale_y_log10(labels = scales::comma)
```

## Unweighted 2017 Monthly Hyads

**Permian Basin**

```{r, warning=F, message=F}
color_palette <- c("#274E1D","#58A735", "#91D846", "#FAF856", "#E5983B", "#E75B2F", "#B83364", "#8A32CA", "#4D97F2", "#2C39F4")
levels_unweighted <- c(0, seq(1000, 120000, length.out=10))
bplot_unweighted <- data.frame(xmin=levels_unweighted[1:10],
                               xmax=levels_unweighted[2:11], 
                               colors=color_palette)

plots <- list()

for(ym_ in unique(hyads_months$ym)) {
  hyads_sf <- tracts_sf %>% 
    left_join(
      filter(hyads_months, ym == ym_, basin_ID == "Permian Basin")
    ) %>% 
    filter(extent %in% c("Permian Basin", "Bend Arch-Fort Worth Basin"))
  
  year_ = unique(na.omit(hyads_sf$year))
  month_ = unique(na.omit(hyads_sf$month))
  
   map <- hyads_sf %>% 
    ggplot() +
    geom_sf(aes(fill = cut(unweighted_hyads, breaks = levels_unweighted)), size = 0) +
    scale_fill_manual(values = color_palette) +
    theme_map() +
    theme(legend.position = "none") + 
    labs(title = paste("year", year_, "month", month_))
  
   box <- hyads_sf %>% 
     st_drop_geometry() %>% 
     ggplot() +
     geom_rect(data = bplot_unweighted, 
               aes(xmin=xmin, xmax=xmax, ymin=-Inf, ymax=Inf, fill=colors), alpha = 0.5) + 
     geom_boxplot(aes(unweighted_hyads), alpha=.2) +
     geom_point(aes(x=min(unweighted_hyads, na.rm = T), y=0), shape=15) +
     geom_point(aes(x=max(unweighted_hyads, na.rm = T), y=0), shape=17) + 
     scale_fill_manual(values = bplot_unweighted$colors, breaks = bplot_unweighted$colors) + 
     scale_x_sqrt() + 
     theme_bw() +
    theme(axis.ticks.y = element_blank(),
          axis.text.y = element_blank(),
          axis.title = element_blank(),
          panel.grid.major.y = element_blank(), 
          panel.grid.minor.y = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.border = element_blank(),
          axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
          legend.position = "none"
    )
   
   plots[[ym_]] <- cowplot::plot_grid(box, map, nrow = 2, rel_heights = c(0.2, 0.8))
}
plots
```

**Gulf Coast Basins**

```{r, warning=F, message=F}
color_palette <- c("#274E1D","#58A735", "#91D846", "#FAF856", "#E5983B", "#E75B2F", "#B83364", "#8A32CA", "#4D97F2", "#2C39F4")
levels_unweighted <- c(0, seq(700, 65000, length.out=10))
bplot_unweighted <- data.frame(xmin=levels_unweighted[1:10],
                               xmax=levels_unweighted[2:11], 
                               colors=color_palette)

plots <- list()

for(ym_ in unique(hyads_months$ym)) {
  hyads_sf <- tracts_sf %>% 
    left_join(
      filter(hyads_months, ym == ym_, basin_ID == "Gulf Coast Basins")
    ) %>% 
    filter(extent %in% c("Gulf Coast Basins", "Bend Arch-Fort Worth Basin"))
  
  year_ = unique(na.omit(hyads_sf$year))
  month_ = unique(na.omit(hyads_sf$month))
  
   map <- hyads_sf %>% 
    ggplot() +
    geom_sf(aes(fill = cut(unweighted_hyads, breaks = levels_unweighted)), size = 0) +
    scale_fill_manual(values = color_palette) +
    theme_map() +
    theme(legend.position = "none") + 
    labs(title = paste("year", year_, "month", month_))
  
   box <- hyads_sf %>% 
     st_drop_geometry() %>% 
     ggplot() +
     geom_rect(data = bplot_unweighted, 
               aes(xmin=xmin, xmax=xmax, ymin=-Inf, ymax=Inf, fill=colors), alpha = 0.5) + 
     geom_boxplot(aes(unweighted_hyads), alpha=.2) +
     geom_point(aes(x=min(unweighted_hyads, na.rm = T), y=0), shape=15) +
     geom_point(aes(x=max(unweighted_hyads, na.rm = T), y=0), shape=17) + 
     scale_fill_manual(values = bplot_unweighted$colors, breaks = bplot_unweighted$colors) + 
     scale_x_sqrt() + 
     theme_bw() +
    theme(axis.ticks.y = element_blank(),
          axis.text.y = element_blank(),
          axis.title = element_blank(),
          panel.grid.major.y = element_blank(), 
          panel.grid.minor.y = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.border = element_blank(),
          axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
          legend.position = "none"
    )
   
   plots[[ym_]] <- cowplot::plot_grid(box, map, nrow = 2, rel_heights = c(0.2, 0.8))
}
plots
```

## Weighted 2017 Monthly Hyads

**Permian Basin**

```{r, warning=F, message=F}
color_palette <- c("#274E1D","#58A735", "#91D846", "#FAF856", "#E5983B", "#E75B2F", "#B83364", "#8A32CA", "#4D97F2", "#2C39F4")
levels_weighted <- c(0, seq(67000, 3.5e7, length.out=10))
bplot_weighted <- data.frame(xmin=levels_weighted[1:10],
                             xmax=levels_weighted[2:11],
                             colors=color_palette)

plots <- list()

for(ym_ in unique(hyads_months$ym)) {
  hyads_sf <- tracts_sf %>% 
    left_join(
      filter(hyads_months, ym == ym_, basin_ID == "Permian Basin")
    ) %>% 
    filter(extent %in% c("Permian Basin", "Bend Arch-Fort Worth Basin"))
  
  year_ = unique(na.omit(hyads_sf$year))
  month_ = unique(na.omit(hyads_sf$month))
  
   map <- hyads_sf %>% 
    ggplot() +
    geom_sf(aes(fill = cut(weighted_hyads, breaks = levels_weighted)), size = 0) +
    scale_fill_manual(values = color_palette) +
    theme_map() +
    theme(legend.position = "none") + 
    labs(title = paste("year", year_, "month", month_))
  
   box <- hyads_sf %>% 
     st_drop_geometry() %>% 
     ggplot() +
     geom_rect(data = bplot_weighted, 
               aes(xmin=xmin, xmax=xmax, ymin=-Inf, ymax=Inf, fill=colors), alpha = 0.5) + 
     geom_boxplot(aes(weighted_hyads), alpha=.2) +
     geom_point(aes(x=min(weighted_hyads, na.rm = T), y=0), shape=15) +
     geom_point(aes(x=max(weighted_hyads, na.rm = T), y=0), shape=17) + 
     scale_fill_manual(values = bplot_weighted$colors, breaks = bplot_weighted$colors) + 
     scale_x_sqrt() + 
     theme_bw() +
    theme(axis.ticks.y = element_blank(),
          axis.text.y = element_blank(),
          axis.title = element_blank(),
          panel.grid.major.y = element_blank(), 
          panel.grid.minor.y = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.border = element_blank(),
          axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
          legend.position = "none"
    )
   
   plots[[ym_]] <- cowplot::plot_grid(box, map, nrow = 2, rel_heights = c(0.2, 0.8))
}
plots
```

**Gulf Coast Basins**

```{r, warning=F, message=F}
color_palette <- c("#274E1D","#58A735", "#91D846", "#FAF856", "#E5983B", "#E75B2F", "#B83364", "#8A32CA", "#4D97F2", "#2C39F4")
levels_weighted <- c(0, seq(23000, 3.8e6, length.out=10))
bplot_weighted <- data.frame(xmin=levels_weighted[1:10],
                             xmax=levels_weighted[2:11],
                             colors=color_palette)

plots <- list()

for(ym_ in unique(hyads_months$ym)) {
  hyads_sf <- tracts_sf %>% 
    left_join(
      filter(hyads_months, ym == ym_, basin_ID == "Gulf Coast Basins")
    ) %>% 
    filter(extent %in% c("Gulf Coast Basins", "Bend Arch-Fort Worth Basin"))
  
  year_ = unique(na.omit(hyads_sf$year))
  month_ = unique(na.omit(hyads_sf$month))
  
   map <- hyads_sf %>% 
    ggplot() +
    geom_sf(aes(fill = cut(weighted_hyads, breaks = levels_weighted)), size = 0) +
    scale_fill_manual(values = color_palette) +
    theme_map() +
    theme(legend.position = "none") + 
    labs(title = paste("year", year_, "month", month_))
  
   box <- hyads_sf %>% 
     st_drop_geometry() %>% 
     ggplot() +
     geom_rect(data = bplot_weighted, 
               aes(xmin=xmin, xmax=xmax, ymin=-Inf, ymax=Inf, fill=colors), alpha = 0.5) + 
     geom_boxplot(aes(weighted_hyads), alpha=.2) +
     geom_point(aes(x=min(weighted_hyads, na.rm = T), y=0), shape=15) +
     geom_point(aes(x=max(weighted_hyads, na.rm = T), y=0), shape=17) + 
     scale_fill_manual(values = bplot_weighted$colors, breaks = bplot_weighted$colors) + 
     scale_x_sqrt() + 
     theme_bw() +
    theme(axis.ticks.y = element_blank(),
          axis.text.y = element_blank(),
          axis.title = element_blank(),
          panel.grid.major.y = element_blank(), 
          panel.grid.minor.y = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.border = element_blank(),
          axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
          legend.position = "none"
    )
   
   plots[[ym_]] <- cowplot::plot_grid(box, map, nrow = 2, rel_heights = c(0.2, 0.8))
}
plots
```

## Yearly Hyads

```{r}
links <- read_rds("../data/jobs_output/linked_counties_2015_7_8.rds") |>
  rbind(read_rds("../data/jobs_output/linked_counties_2015_9_10.rds")) |>
  rbind(read_rds("../data/jobs_output/linked_counties_2015_11_12.rds")) |>
  rbind(read_rds("../data/jobs_output/linked_counties_2016_1_2.rds")) |>
  rbind(read_rds("../data/jobs_output/linked_counties_2016_3_4.rds")) |>
  #rbind(read_rds("../data/jobs_output/linked_counties_2016_5_6.rds")) |>
  rbind(read_rds("../data/jobs_output/linked_counties_2016_7_8.rds")) |>
  #rbind(read_rds("../data/jobs_output/linked_counties_2016_9_10.rds")) |>
  rbind(read_rds("../data/jobs_output/linked_counties_2016_11_12.rds")) |>
  rbind(read_rds("../data/jobs_output/linked_counties_2017_1_2.rds")) |>
  rbind(read_rds("../data/jobs_output/linked_counties_2017_3_4.rds")) |>
  rbind(read_rds("../data/jobs_output/linked_counties_2017_5_6.rds")) |>
  rbind(read_rds("../data/jobs_output/linked_counties_2017_7_8.rds")) |>
  rbind(read_rds("../data/jobs_output/linked_counties_2017_9_10.rds")) |>
  rbind(read_rds("../data/jobs_output/linked_counties_2017_11_12.rds")) |>
  #rbind(read_rds("../data/jobs_output/linked_counties_2018_1_2.rds")) |>
  rbind(read_rds("../data/jobs_output/linked_counties_2018_3_4.rds")) |>
  rbind(read_rds("../data/jobs_output/linked_counties_2018_5_6.rds")) |>
  rbind(read_rds("../data/jobs_output/linked_counties_2018_7_8.rds")) |>
  rbind(read_rds("../data/jobs_output/linked_counties_2018_9_10.rds")) |>
  rbind(read_rds("../data/jobs_output/linked_counties_2018_11_12.rds")) |>
  #rbind(read_rds("../data/jobs_output/linked_counties_2019_1_2.rds")) |>
  rbind(read_rds("../data/jobs_output/linked_counties_2019_3_4.rds")) |>
  rbind(read_rds("../data/jobs_output/linked_counties_2019_5_6.rds")) |>
  rbind(read_rds("../data/jobs_output/linked_counties_2019_7_8.rds")) |>
  rbind(read_rds("../data/jobs_output/linked_counties_2019_9_10.rds")) |>
  rbind(read_rds("../data/jobs_output/linked_counties_2019_11_12.rds")) |>
  rbind(read_rds("../data/jobs_output/linked_counties_2020_1_2.rds")) |>
  rbind(read_rds("../data/jobs_output/linked_counties_2020_3_4.rds")) |>
  rbind(read_rds("../data/jobs_output/linked_counties_2020_5_6.rds")) |>
  rbind(read_rds("../data/jobs_output/linked_counties_2020_7_8.rds")) |>
  rbind(read_rds("../data/jobs_output/linked_counties_2020_9_10.rds")) |>
  rbind(read_rds("../data/jobs_output/linked_counties_2020_11_12.rds"))

links %<>% 
  rename(GEOID = geoid, hyads = N, ym = month)  %>% 
  mutate(year = as.integer(str_sub(ym, 1, 4)),
         month = as.integer(str_sub(ym, 5, -1)),
         date = ymd(sprintf("%04d%02d01", year, month)))
```

```{r}
xx <- disperser_input %>% 
  distinct(ID, year, month, start_day, w) %>% 
  group_by(ID, year, month) %>% 
  summarise(w = sum(w))  %>% 
  left_join(
    tracts_sf %>% 
      st_drop_geometry() %>% 
      rename(ID = GEOID) %>% 
      dplyr::select(ID, basin) 
  ) %>% 
  rename(basin_ID = basin)

hyads_years <- left_join(links, xx) %>% 
  group_by(GEOID, year, basin_ID) %>% 
  summarise(
    unweighted_hyads = sum(hyads),
    weighted_hyads = sum(w * hyads)
  )
```

* Unweighed hyads values summary in each basin for all tracts-year with positive exposure

```{r}
tapply(hyads_years$unweighted_hyads, hyads_years$basin_ID, summary)
```

```{r}
hyads_years %>% 
  ggplot() +
  geom_violin(aes(x=basin_ID, y=unweighted_hyads)) + 
  scale_y_log10(labels = scales::comma)
```

* Weighed hyads values summary in each basin for all tracts-year with positive exposure

```{r}
tapply(hyads_years$weighted_hyads, hyads_years$basin_ID, summary)
```

```{r}
hyads_years %>% 
  ggplot() +
  geom_violin(aes(x=basin_ID, y=weighted_hyads)) + 
  scale_y_log10(labels = scales::comma)
```


## Unweighted Yearly Hyads

**Permian Basin**

```{r, warning=F, message=F}
color_palette <- c("#274E1D","#58A735", "#91D846", "#FAF856", "#E5983B", "#E75B2F", "#B83364", "#8A32CA", "#4D97F2", "#2C39F4")
levels_unweighted <- c(0, seq(5000, 1.1e6, length.out=10))
bplot_unweighted <- data.frame(xmin=levels_unweighted[1:10],
                               xmax=levels_unweighted[2:11], 
                               colors=color_palette)

plots <- list()

for(year_ in unique(hyads_years$year)) {
  hyads_sf <- tracts_sf %>% 
    left_join(
      filter(hyads_years, year == year_, basin_ID == "Permian Basin")
    ) %>% 
    filter(extent %in% c("Permian Basin", "Bend Arch-Fort Worth Basin"))
  
   map <- hyads_sf %>% 
    ggplot() +
    geom_sf(aes(fill = cut(unweighted_hyads, breaks = levels_unweighted)), size = 0) +
    scale_fill_manual(values = color_palette) +
    theme_map() +
    theme(legend.position = "none") +
    labs(title = paste("year", year_))
  
   box <- hyads_sf %>% 
     st_drop_geometry() %>% 
     ggplot() +
     geom_rect(data = bplot_unweighted, 
               aes(xmin=xmin, xmax=xmax, ymin=-Inf, ymax=Inf, fill=colors), alpha = 0.5) + 
     geom_boxplot(aes(unweighted_hyads), alpha=.2) +
     geom_point(aes(x=min(unweighted_hyads, na.rm = T), y=0), shape=15) +
     geom_point(aes(x=max(unweighted_hyads, na.rm = T), y=0), shape=17) + 
     scale_fill_manual(values = bplot_unweighted$colors, breaks = bplot_unweighted$colors) + 
     scale_x_sqrt() + 
     theme_bw() +
    theme(axis.ticks.y = element_blank(),
          axis.text.y = element_blank(),
          axis.title = element_blank(),
          panel.grid.major.y = element_blank(), 
          panel.grid.minor.y = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.border = element_blank(),
          axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
          legend.position = "none"
    )
   
   plots[[as.character(year_)]] <- cowplot::plot_grid(box, map, nrow = 2, rel_heights = c(0.2, 0.8))
}
plots
```

**Gulf Coast Basins**

```{r, warning=F, message=F}
color_palette <- c("#274E1D","#58A735", "#91D846", "#FAF856", "#E5983B", "#E75B2F", "#B83364", "#8A32CA", "#4D97F2", "#2C39F4")
levels_unweighted <- c(0, seq(7000, 650000, length.out=10))
bplot_unweighted <- data.frame(xmin=levels_unweighted[1:10],
                               xmax=levels_unweighted[2:11], 
                               colors=color_palette)

plots <- list()

for(year_ in unique(hyads_years$year)) {
  hyads_sf <- tracts_sf %>% 
    left_join(
      filter(hyads_years, year == year_, basin_ID == "Gulf Coast Basins")
    ) %>% 
    filter(extent %in% c("Gulf Coast Basins", "Bend Arch-Fort Worth Basin"))
  
   map <- hyads_sf %>% 
    ggplot() +
    geom_sf(aes(fill = cut(unweighted_hyads, breaks = levels_unweighted)), size = 0) +
    scale_fill_manual(values = color_palette) +
    theme_map() +
    theme(legend.position = "none") + 
    labs(title = paste("year", year_))
  
   box <- hyads_sf %>% 
     st_drop_geometry() %>% 
     ggplot() +
     geom_rect(data = bplot_unweighted, 
               aes(xmin=xmin, xmax=xmax, ymin=-Inf, ymax=Inf, fill=colors), alpha = 0.5) + 
     geom_boxplot(aes(unweighted_hyads), alpha=.2) +
     geom_point(aes(x=min(unweighted_hyads, na.rm = T), y=0), shape=15) +
     geom_point(aes(x=max(unweighted_hyads, na.rm = T), y=0), shape=17) + 
     scale_fill_manual(values = bplot_unweighted$colors, breaks = bplot_unweighted$colors) + 
     scale_x_sqrt() + 
     theme_bw() +
    theme(axis.ticks.y = element_blank(),
          axis.text.y = element_blank(),
          axis.title = element_blank(),
          panel.grid.major.y = element_blank(), 
          panel.grid.minor.y = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.border = element_blank(),
          axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
          legend.position = "none"
    )
   
   plots[[as.character(year_)]] <- cowplot::plot_grid(box, map, nrow = 2, rel_heights = c(0.2, 0.8))
}
plots
```

## Weighted Yearly Hyads

**Permian Basin**

```{r, warning=F, message=F}
color_palette <- c("#274E1D","#58A735", "#91D846", "#FAF856", "#E5983B", "#E75B2F", "#B83364", "#8A32CA", "#4D97F2", "#2C39F4")
levels_weighted <- c(0, seq(650000, 446e6, length.out=10))
bplot_weighted <- data.frame(xmin=levels_weighted[1:10],
                             xmax=levels_weighted[2:11],
                             colors=color_palette)

plots <- list()

for(year_ in unique(hyads_years$year)) {
  hyads_sf <- tracts_sf %>% 
    left_join(
      filter(hyads_years, year == year_, basin_ID == "Permian Basin")
    ) %>% 
    filter(extent %in% c("Permian Basin", "Bend Arch-Fort Worth Basin"))
  
   map <- hyads_sf %>% 
    ggplot() +
    geom_sf(aes(fill = cut(weighted_hyads, breaks = levels_weighted)), size = 0) +
    scale_fill_manual(values = color_palette) +
    theme_map() +
    theme(legend.position = "none") + 
    labs(title = paste("year", year_))
  
   box <- hyads_sf %>% 
     st_drop_geometry() %>% 
     ggplot() +
     geom_rect(data = bplot_weighted, 
               aes(xmin=xmin, xmax=xmax, ymin=-Inf, ymax=Inf, fill=colors), alpha = 0.5) + 
     geom_boxplot(aes(weighted_hyads), alpha=.2) +
     geom_point(aes(x=min(weighted_hyads, na.rm = T), y=0), shape=15) +
     geom_point(aes(x=max(weighted_hyads, na.rm = T), y=0), shape=17) + 
     scale_fill_manual(values = bplot_weighted$colors, breaks = bplot_weighted$colors) + 
     scale_x_sqrt() + 
     theme_bw() +
    theme(axis.ticks.y = element_blank(),
          axis.text.y = element_blank(),
          axis.title = element_blank(),
          panel.grid.major.y = element_blank(), 
          panel.grid.minor.y = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.border = element_blank(),
          axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
          legend.position = "none"
    )
   
   plots[[as.character(year_)]] <- cowplot::plot_grid(box, map, nrow = 2, rel_heights = c(0.2, 0.8))
}
plots
```

**Gulf Coast Basins**

```{r, warning=F, message=F}
color_palette <- c("#274E1D","#58A735", "#91D846", "#FAF856", "#E5983B", "#E75B2F", "#B83364", "#8A32CA", "#4D97F2", "#2C39F4")
levels_weighted <- c(0, seq(320000, 47e6, length.out=10))
bplot_weighted <- data.frame(xmin=levels_weighted[1:10],
                             xmax=levels_weighted[2:11],
                             colors=color_palette)

plots <- list()

for(year_ in unique(hyads_years$year)) {
  hyads_sf <- tracts_sf %>% 
    left_join(
      filter(hyads_years, year == year_, basin_ID == "Gulf Coast Basins")
    ) %>% 
    filter(extent %in% c("Gulf Coast Basins", "Bend Arch-Fort Worth Basin"))
  
   map <- hyads_sf %>% 
    ggplot() +
    geom_sf(aes(fill = cut(weighted_hyads, breaks = levels_weighted)), size = 0) +
    scale_fill_manual(values = color_palette) +
    theme_map() +
    theme(legend.position = "none") + 
    labs(title = paste("year", year_))
  
   box <- hyads_sf %>% 
     st_drop_geometry() %>% 
     ggplot() +
     geom_rect(data = bplot_weighted, 
               aes(xmin=xmin, xmax=xmax, ymin=-Inf, ymax=Inf, fill=colors), alpha = 0.5) + 
     geom_boxplot(aes(weighted_hyads), alpha=.2) +
     geom_point(aes(x=min(weighted_hyads, na.rm = T), y=0), shape=15) +
     geom_point(aes(x=max(weighted_hyads, na.rm = T), y=0), shape=17) + 
     scale_fill_manual(values = bplot_weighted$colors, breaks = bplot_weighted$colors) + 
     scale_x_sqrt() + 
     theme_bw() +
    theme(axis.ticks.y = element_blank(),
          axis.text.y = element_blank(),
          axis.title = element_blank(),
          panel.grid.major.y = element_blank(), 
          panel.grid.minor.y = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.border = element_blank(),
          axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
          legend.position = "none"
    )
   
   plots[[as.character(year_)]] <- cowplot::plot_grid(box, map, nrow = 2, rel_heights = c(0.2, 0.8))
}
plots
```
