# Parcels checkpoint

```{r, warning=F, message=F}
source("../lib/polygon_parcels_parallel.R")

library(tidyverse)
library(magrittr)
library(lubridate)
library(data.table)
library(fst)
library(sf)
library(gridExtra)
library(cowplot)
library(viridis)
library(ggthemes)
library(knitr)

disperser_input <- read_rds("../data/jobs_input/disperser_input.rds")
polygons_sf <- st_read("../data/input/tl_2016_48_tract/tl_2016_48_tract.shp") # <- for polygon_parcel input
tracts_sf <- read_rds("../data/preprocessed/tracts_sf.rds") # <- for analysis
```

## check 1

* check disperser was able to run simulations for all emissions in disperser_input (compare with `ls | wc` at the simulations location)

```{r}
#### number of files disperser will create for each year month
disperser_input %>% 
  group_by(year, month) %>% 
  summarise(n = n()) %>% DT::datatable()
```

## check 2

* validate that the number of parcels that are dispersed in each simulation run are counted in the polygon_parcel function

```{r}
#### set params for run_polygon_parcels
polygons_sf %<>% 
  filter(STATEFP == "48")  %>% 
  mutate(GEOID = as.character(GEOID)) %>% 
  rename(id = GEOID)
polygons_sf <- polygons_sf[, 'id']
hysp_dir = "../data/jobs_output/vanilla/hysplit"
mc.cores = parallel::detectCores()

range = which(disperser_input$start_day == as.Date("2018-01-06") & 
                disperser_input$start_hour == 2)
input.refs = data.table(disperser_input[range,], stringsAsFactors = FALSE)

run_X <- lapply(1:nrow(input.refs), function(r) input.refs[r])
```

```{r, warning=F, message=F, results='hide'}
res.link = 12000

polygon_parcels <- list()
parcels_count <- c()
plots <- list()
for(X in run_X){
  polygon_parcels_ <- run_polygon_parcels(X = X, 
                                          polygons_sf = polygons_sf, 
                                          hysp_dir = hysp_dir, 
                                          res.link = res.link)
  r <- polygon_parcels_[[1]]
  polygon_parcels[[X$ID]] <- polygon_parcels_[[2]]
  
  parcels_count <- c(parcels_count, sum(polygon_parcels[[X$ID]]$count, na.rm = T))
  parcels_sf <- tracts_sf %>%  
    left_join(rename(polygon_parcels[[X$ID]], GEOID = id)) %>% 
    filter(GEOID %in% polygon_parcels[[X$ID]]$id) %>% 
    mutate(concentration = count / area)

  p1 <- ggplot(parcels_sf) + 
    geom_sf(aes(fill = count), size = 0) + 
    geom_sf(data = (filter(parcels_sf, GEOID == X$ID)), 
            color = "red", fill = NA) +
    scale_fill_viridis(option = "B") +
    theme_map() + 
    theme(legend.position = "none")

  p2 <- ggplot(parcels_sf) + 
    geom_sf(aes(fill = concentration), size = 0) + 
    geom_sf(data = (filter(parcels_sf, GEOID == X$ID)), 
            color = "red", fill = NA) +
    scale_fill_viridis(option = "B") +
    theme_map() + 
    theme(legend.position = "none")

  p3 <- ggplot(parcels_sf) + 
    geom_sf(aes(fill = hyads), size = 0) + 
    geom_sf(data = (filter(parcels_sf, GEOID == X$ID)), 
            color = "red", fill = NA) +
    scale_fill_viridis(option = "B") +
    theme_map() + 
    theme(legend.position = "none")
  
  p4 <- ggplot(parcels_sf) + 
    geom_sf() + 
    geom_sf(data = (filter(parcels_sf, GEOID == X$ID)), 
            color = "red", fill = NA) +
    geom_sf(data = st_as_sf(r), aes(fill = layer), 
            alpha = 0.8, color = "white")  +
    theme_map() + 
    theme(legend.position = "none")
  
  # p4 <- parcels_sf %>%
  #   mutate(concentr_adj = concentration / max(parcels_sf$concentration, na.rm = T),
  #          hyads_adj = hyads / max(parcels_sf$hyads, na.rm = T)) %>%
  #   ggplot() +
  #   geom_point(aes(x=hyads_adj, y=count)) +
  #   geom_point(aes(x=concentr_adj, y=count), col = "red") + 
  #   labs(x = "concentration (red), hyads(black)") 

  plots[[X$ID]] <- plot_grid(p1, p2, p4, p3)
}

polygon_parcels_1 <- rbindlist(polygon_parcels)
```

```{r}
#grid square base
sqrt(as.numeric(st_area(st_as_sf(r)[1, ])) / 1e6) 
```


```{r}
parcels_count
```

## check 3

* visual inspection of counts and raw concentrations and exposure estimates using two values for `res.link` the length of the grid square's sides that are used to compute hyads exposure. The first group uses `res.link=12000` and the second group `res.link=50000`.

### Group 1

Hyads smothes the parcel dispersion and assigns an exposure measure. With `res.link=12000` the exposure looks good.

```{r}
plots[c(1, 5, 22, 23)]
```

Sometimes it is not obvious how the daily exposure estimation is smooth.

```{r}
plots[c(11, 12, 14, 18)]
```

### Group 2

Parameter tuning of grid resolution must balance between grid's square sizes, polygon sizes and sparsity (number of simulated parcels).

```{r, warning=F, message=F, results='hide'}
res.link = 50000

polygon_parcels <- list()
parcels_count <- c()
plots <- list()
for(X in run_X){
  polygon_parcels_ <- run_polygon_parcels(X = X, 
                                          polygons_sf = polygons_sf, 
                                          hysp_dir = hysp_dir, 
                                          res.link = res.link)
  r <- polygon_parcels_[[1]]
  polygon_parcels[[X$ID]] <- polygon_parcels_[[2]]
  
  parcels_count <- c(parcels_count, sum(polygon_parcels[[X$ID]]$count, na.rm = T))
  parcels_sf <- tracts_sf %>%  
    left_join(rename(polygon_parcels[[X$ID]], GEOID = id)) %>% 
    filter(GEOID %in% polygon_parcels[[X$ID]]$id) %>% 
    mutate(concentration = count / area)

  p1 <- ggplot(parcels_sf) + 
    geom_sf(aes(fill = count), size = 0) + 
    geom_sf(data = (filter(parcels_sf, GEOID == X$ID)), 
            color = "red", fill = NA) +
    scale_fill_viridis(option = "B") +
    theme_map() + 
    theme(legend.position = "none")

  p2 <- ggplot(parcels_sf) + 
    geom_sf(aes(fill = concentration), size = 0) + 
    geom_sf(data = (filter(parcels_sf, GEOID == X$ID)), 
            color = "red", fill = NA) +
    scale_fill_viridis(option = "B") +
    theme_map() + 
    theme(legend.position = "none")

  p3 <- ggplot(parcels_sf) + 
    geom_sf(aes(fill = hyads), size = 0) + 
    geom_sf(data = (filter(parcels_sf, GEOID == X$ID)), 
            color = "red", fill = NA) +
    scale_fill_viridis(option = "B") +
    theme_map() + 
    theme(legend.position = "none")
  
  p4 <- ggplot(parcels_sf) + 
    geom_sf() + 
    geom_sf(data = (filter(parcels_sf, GEOID == X$ID)), 
            color = "red", fill = NA) +
    geom_sf(data = st_as_sf(r), aes(fill = layer), 
            alpha = 0.8, color = "white")  +
    theme_map() + 
    theme(legend.position = "none")
  
  # p4 <- parcels_sf %>%
  #   mutate(concentr_adj = concentration / max(parcels_sf$concentration, na.rm = T),
  #          hyads_adj = hyads / max(parcels_sf$hyads, na.rm = T)) %>%
  #   ggplot() +
  #   geom_point(aes(x=hyads_adj, y=count)) +
  #   geom_point(aes(x=concentr_adj, y=count), col = "red") + 
  #   labs(x = "concentration (red), hyads(black)") 

  plots[[X$ID]] <- plot_grid(p1, p2, p4, p3)
}
polygon_parcels_2 <- rbindlist(polygon_parcels)
```

```{r}
#grid square base
sqrt(as.numeric(st_area(st_as_sf(r)[1, ])) / 1e6) 
```

```{r}
plots[c(1, 5, 22, 23)]
```


```{r}
plots[c(11, 12, 14, 18)]
```

## check 4

* inspection of counts of parcels from all locations, its concentration, and hyads exposure in a single day. Group 1 and 2 use different grid resolutions, `res.link=12000` and `res.link=50000`.

Exposure estimates change with grid resolution.

```{r, warning=F, message=F, results='hide'}
flares_sf <- tracts_sf %>%  
  left_join(rename(input.refs, GEOID = ID)) %>% 
  filter(GEOID %in% disperser_input$ID)

p1 <- flares_sf %>% 
  ggplot() + 
  geom_sf(aes(fill = w), size = 0) + 
  scale_fill_viridis(option = "B") +
  theme_map() + 
  theme(legend.position = "none")

polygon_parcels <- polygon_parcels_1

polygon_parcels %<>% 
  group_by(id, w, source) %>% 
  summarise(count = w * sum(count, na.rm = T), 
            hyads = w * hyads)

parcels_sf <- tracts_sf %>%  
  left_join(rename(polygon_parcels, GEOID = id)) %>% 
  filter(GEOID %in% polygon_parcels$id) %>% 
  mutate(concentration = w * count / area)

p2 <- parcels_sf %>%  
  ggplot() + 
  geom_sf(aes(fill = count), size = 0) + 
  scale_fill_viridis(option = "B") +
  theme_map() + 
  theme(legend.position = "none")

p3 <- parcels_sf %>% 
  ggplot() + 
  geom_sf(aes(fill = concentration), size = 0) + 
  scale_fill_viridis(option = "B") +
  theme_map() + 
  theme(legend.position = "none")

p4 <- parcels_sf %>%  
  ggplot() + 
  geom_sf(aes(fill = hyads), size = 0) + 
  scale_fill_viridis(option = "B") +
  theme_map() + 
  theme(legend.position = "none")

polygon_parcels <- polygon_parcels_2

polygon_parcels %<>% 
  group_by(id, w, source) %>% 
  summarise(count = w * sum(count, na.rm = T), 
            hyads = w * hyads)

parcels_sf <- tracts_sf %>%  
  left_join(rename(polygon_parcels, GEOID = id)) %>% 
  filter(GEOID %in% polygon_parcels$id) %>% 
  mutate(concentration = w * count / area)

p5 <- parcels_sf %>%  
  ggplot() + 
  geom_sf(aes(fill = hyads), size = 0) + 
  scale_fill_viridis(option = "B") +
  theme_map() + 
  theme(legend.position = "none")
  
plot_grid(p1, p2, p3, p4, p5)
```
